A novel distributed nature-inspired algorithm for solving optimization problems (Life-Cycle Algorithm)\thanks{Supported by organization x.}

### 2021-07-15 paper.tex
Abstarct updated
Line spaces.

\begin{document}
%
\title{(Biological) Life-Cycle Algorithm\thanks{Supported by organization x.}}
%
%\titlerunning{Abbreviated paper title}
% If the paper title is too long for the running head, you can set
% an abbreviated paper title here
%
\author{First Author\inst{1}\orcidID{0000-1111-2222-3333} \and
Second Author\inst{2,3}\orcidID{1111-2222-3333-4444} \and
Third Author\inst{3}\orcidID{2222--3333-4444-5555}}
%
\authorrunning{F. Author et al.}
% First names are abbreviated in the running head.
% If there are more than two authors, 'et al.' is used.
%
\institute{Princeton University, Princeton NJ 08544, USA \and
Springer Heidelberg, Tiergartenstr. 17, 69121 Heidelberg, Germany
\email{lncs@springer.com}\\
\url{http://www.springer.com/gp/computer-science/lncs} \and
ABC Institute, Rupert-Karls-University Heidelberg, Heidelberg, Germany\\
\email{\{abc,lncs\}@uni-heidelberg.de}}
%
\maketitle              % typeset the header of the contribution
%
\begin{abstract}
%The abstract should briefly summarize the contents of the paper in 150--250 words.

% ----------------------------------
% [History Drafts]
% [Draft 1] This paper is a proposal for a nature-inspired algorithm that seeks to solve the basic GA problem OneMax. This is a distributed algorithm in all its conception, where the idea is that its mechanism can operate from different containers (or equipment) independently, eliminating waiting times between processes. This algorithm emphasizes the use of cloud computing available resources. Its mechanism is composed of birth, growth, reproduction, and death, where each one of them works concurrently and asynchronously on a population that evolves constantly. This strategy takes a similar focus as the study of bacteria growth in microbiology, where using a microscope, we can observe and analyze the evolution of a population over time. This implementation also can be useful, as an introductory example to the native cloud computing programming, inspired by the GA algorithm operation mechanics. One difference from the GA is in the reproduction mechanism, which is flexible to work in parallel with several strategies simultaneously, for example, tourney selection, random selection of couples in the population, and couple selection with a random mating individual outside of the population.
% ----------------------------------

Several bio-inspired algorithms use population evolution as analogies of
nature. In this paper, we followed a strategy that takes a similar approach as
the study of bacteria growth in microbiology, where using a microscope, we can
observe and analyze the evolution of a population over time. We present an
algorithm inspired by the biological life-cycle of animal species, which
consists of several stages: birth, growth, reproduction, and death. As in
nature, we intend to execute all these stages in parallel and asynchronously on
a population that evolves constantly. In this paper, we present a novel distributed nature-inspired algorithm for
solving optimization problems. From the ground up, we designed the algorithm as
a cloud-native solution using the cloud available resources to divide the
processing workload, among several computers or running the algorithm as a
cloud service. The algorithm works concurrently and asynchronously on a
constantly evolving population, using different computers (or containers)
independently, eliminating waiting times between processes. This algorithm 
seeks to imitate the natural life cycle, where new individuals
are born at any moment and mature over time, where they age and suffer
mutations throughout their lives. In reproduction, couples match by mutual
attraction, where they may have offspring. Death can happen to everyone: from a
newborn to an aged adult, where the individual's fitness will impact their
longevity. As a proof-of-concept, we implemented the algorithm with Docker
containers by solving the OneMax problem comparing it with a basic (sequential) GA 
algorithm, where it showed favorable and promising results.

>>>>

\begin{document}
%
\title{A novel distributed nature-inspired algorithm for solving optimization problems (Life-Cycle Algorithm)\thanks{Supported by organization x.}}
%
%\titlerunning{Abbreviated paper title}
% If the paper title is too long for the running head, you can set
% an abbreviated paper title here
%
\author{First Author\inst{1}\orcidID{0000-1111-2222-3333} \and
Second Author\inst{2,3}\orcidID{1111-2222-3333-4444} \and
Third Author\inst{3}\orcidID{2222--3333-4444-5555}}
%
\authorrunning{F. Author et al.}
% First names are abbreviated in the running head.
% If there are more than two authors, 'et al.' is used.
%
\institute{Princeton University, Princeton NJ 08544, USA \and
Springer Heidelberg, Tiergartenstr. 17, 69121 Heidelberg, Germany
\email{lncs@springer.com}\\
\url{http://www.springer.com/gp/computer-science/lncs} \and
ABC Institute, Rupert-Karls-University Heidelberg, Heidelberg, Germany\\
\email{\{abc,lncs\}@uni-heidelberg.de}}
%
\maketitle              % typeset the header of the contribution
%
\begin{abstract}
%The abstract should briefly summarize the contents of the paper in 150--250 words.

Several bio-inspired algorithms use population evolution as analogies of
nature. In this paper, we present an algorithm inspired by the biological
life-cycle of animal species, which consists of several stages: birth, growth,
reproduction, and death. As in nature, we intend to execute all these stages in
parallel and asynchronously on a population that evolves constantly. From the
ground up, we designed the algorithm as a cloud-native solution using the cloud
available resources to divide the processing workload, among several computers
or running the algorithm as a cloud service. The algorithm works concurrently
and asynchronously on a constantly evolving population, using different
computers (or containers) independently, eliminating waiting times between
processes. This algorithm seeks to imitate the natural life cycle, where new
individuals are born at any moment and mature over time, where they age and
suffer mutations throughout their lives. In reproduction, couples match by
mutual attraction, where they may have offspring. Death can happen to everyone:
from a newborn to an aged adult, where the individual's fitness will impact
their longevity. As a proof-of-concept, we implemented the algorithm with
Docker containers by solving the OneMax problem comparing it with a basic
(sequential) GA algorithm, where it showed favorable and promising results.
